Analysis of bulk void regions

### 2014-07-02 cosmic_voids.tex
New percolation analysis, codes, figures and pdf
References and new format of plots

The spatial distribution of galaxies describes a web-like pattern, the 
so-called cosmic web. Today it is understood that such configuration is 
driven by gravitational instabilities. ...

Relevant information about previous works and current state of the art.

@@

As it was previously mentioned, we use an unconstrained cosmological 
simulation, the Bolshoi simulation, to identify the possible large scale 
environment of the Local Group. This is a similar approach to the one already 
used by \SRKED{[reference here]}.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify halos with two algorithms, the Friends-of-Friends \SRKED{
[reference here]} algorithm and the Bound Density Maximum algorithm.

@@

\bibliographystyle{mn2e}
\bibliography{references}

@@

@@

%.........................................................................
%FIGURE 3: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 4: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

>>>>

Cosmic voids are one of the more striking features of the Mpc universe, 
where they are complementary to the filamentary 
\cite{Neyrinck08}

@@

We use here an unconstrained cosmological simulation, the Bolshoi 
simulation, to identify the possible large scale environment and 
cosmological voids.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify catalogues of halos through the Bound Density Maximum 
algorithm.

@@

\bibliographystyle{latex/mn2e}
\bibliography{references}

@@

%.........................................................................
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 3: Percolation Analysis
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.6\textheight]{./figures/voids_percolation_analysis.pdf}

%.........................................................................
%FIGURE 4: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 5: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering
